Switch equivalence and weak prime domains for fusions

### 2023-12-28 fusione.tex

	We are left with the case $i=n+1$. Let us compute
	\begin{align*}
		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=p'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
	\end{align*}
	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad p'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad p'_2\circ \iota'_{2, G'_{2, 0}}=
	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
	to get
	\begin{align*}
		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
	\end{align*}
\end{itemize}
The thesis now follows at once.	
\end{proof}

\begin{corollary}\label{cor:presuffix}
	\todo{prefisso e suffisso}
\end{corollary}
\begin{proof}
	contenuto...
\end{proof}

>>>>

	We are left with the case $i=n+1$. Let us compute
	\begin{align*}
		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=p'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
	\end{align*}
	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad p'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad p'_2\circ \iota'_{2, G'_{2, 0}}=
	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
	to get
	\begin{align*}
		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
	\end{align*}
\end{itemize}
6The thesis now follows at once.	
\end{proof}

\begin{corollary}\label{cor:presuffix} Let $(\X, \R)$ be a consuming left linear DPO-rewriting system.  Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$. Suppose that $\sigma:[0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.  If $\tau:[0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D_1}, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$, then:
	\begin{enumerate}
		\item the permutation
		\[\varrho:[0,l_2-1]\to [0, l_2-1] \qquad i \mapsto \sigma(i+l_1)-l_1\]
		is a consistent one;
		\item for every $i\in [0,l_1-1]$, $\sigma(i)=\tau(i)$.
	\end{enumerate}
\end{corollary}
\begin{proof}\begin{enumerate}
		\item 
		\item By \Cref{prop:sum} and the previous point $\tau + \varrho$ is a consistent permutation between   $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$. Hence, by \Cref{cor:unique} we have
		\[\tau+\varrho=\sigma\]
		From which the thesis follows.\qedhere 
	\end{enumerate}
\end{proof}
